PANCHANGE_descriptives

### 2020-11-05 PANCHANGE_exclusion_descriptives.Rmd
Corrected the impute and correlations chunks

#SB - Impute no change prepandemic scores

I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores. Hence, if this was the case, I imputed their baseline score. However, this interpretation could be wrong.

Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate). This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?

@@

#Edit the gad sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is

impute_dat <- dat %>% 
  mutate(gad.sum_score_retro = 
           if_else(is.na(dat$gad.sum_score_retro), dat$gad.sum_score_base, dat$gad.sum_score_retro))

@@

#Edit the phq sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is

impute_dat <- dat %>% 
  mutate(phq.sum_score_retro = 
           if_else(is.na(dat$phq.sum_score_retro), dat$phq.sum_score_base, dat$phq.sum_score_retro))

@@

```{r Impute for ocir measure}

#Visualise the ocir summary scores for baseline and retro
head(dat$ocir.sum_score_base, 40)
head(dat$ocir.sum_score_retro, 40)

#Edit the ocir sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is

impute_dat <- dat %>% 
  mutate(ocir.sum_score_retro = 
           if_else(is.na(dat$ocir.sum_score_retro), dat$ocir.sum_score_base,                                     dat$ocir.sum_score_retro))

#Check that the Na's have been replaced with duplicated baseline sum scores
head(impute_dat$ocir.sum_score_base, 40)
head(impute_dat$ocir.sum_score_retro, 40)

```{r Impute for pcl measure}

#Visualise the pcl summary scores for baseline and retro
head(dat$pcl.sum_score_base, 30)
head(dat$pcl.sum_score_retro, 30)

#Edit the pcl sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is

impute_dat <- dat %>% 
  mutate(pcl.sum_score_retro = 
           if_else(is.na(dat$pcl.sum_score_retro), dat$pcl.sum_score_base, dat$pcl.sum_score_retro))

#Check that the Na's have been replaced with duplicated baseline sum scores
head(impute_dat$pcl.sum_score_base, 30)
head(impute_dat$pcl.sum_score_retro, 30)

#SB - Baseline survey completion (N per month)

This is a summary of the amount of pt's completing the baseline survey per month

@@

#SB - Correlation between retropsective impute and prepan

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "pcl.sum_score_prepan",
    "pcl.sum_score_retro",
    "ocir.sum_score_prepan",
    "ocir.sum_score_retro",
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)

>>>>

#Impute no change prepandemic scores

@@

#Visualise the gad pandemic feelings variables
head(dat$gad.pandemic_felt_feelings, 10)
head(dat$gad.pandemic_felt_feelings_numeric, 10)

#Edit the gad sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.

impute_dat <- dat %>% 
  mutate(gad.sum_score_retro =
           case_when(gad.pandemic_felt_feelings == "No different" & is.na(gad.sum_score_retro)                      ~ gad.sum_score_base,
                     !is.na(gad.sum_score_retro) ~ gad.sum_score_retro))

@@

#Visualise the phq pandemic feelings variables
head(dat$phq.pandemic_felt_feelings, 10)
head(dat$phq.pandemic_felt_feelings_numeric, 10)

#Edit the phq sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.

impute_dat <- dat %>% 
  mutate(phq.sum_score_retro =
           case_when(phq.pandemic_felt_feelings == "No different" & is.na(phq.sum_score_retro)                      ~ phq.sum_score_base,
                     !is.na(phq.sum_score_retro) ~ phq.sum_score_retro))

@@

#Baseline survey completion (N per month)

@@

#Correlation between retropsective impute and prepan

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "ocir.sum_score_prepan",
    "ocir.sum_score_retro",
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)
